Counterfactual Training

### 2024-12-18 paper/presenations/slides.qmd
try a bit smalelr

- Trying to distribute: 
    1. Models/experiments across processes and then ...
    2. ... for each model/experiment distribute the counterfactual search across processes.
- Out-of-memory issues, data races, ...
- Multi-processing for models & multi-threading for counterfactual search: low CPU efficiency on DelftBlue (jobs get cancelled).

@@

$$
\ell_{\text{clf}}(f(x),y) + \lambda_{\text{gen}} \ell_{\text{gen}}(x^\prime,x) + \lambda_{\text{adv}} \ell_{\text{clf}}(f(x^\prime),y) + \text{reg}
$$

>>>>

- Trying to distribute: 
    1. Models/experiments across processes.
    2. For each model/experiment distribute the counterfactual search across processes.
- Out-of-memory issues, data races, ...
- Multi-processing for models & multi-threading for counterfactual search: low CPU efficiency on DelftBlue (jobs get cancelled).

@@

$$
\ell_{\text{clf}}(f(x),y) + \lambda_{\text{gen}} \ell_{\text{gen}}(x^\prime,x) + \lambda_{\text{adv}} \ell_{\text{clf}}(f(x^\prime),y) + \text{r}
$$

- $x^\prime$ are counterfactuals of $x$.
- $\ell_{\text{gen}}$ is the difference in energies between observed samples and counterfactuals.
- Counterfactuals are recycled as adversarial examples.

## Training Details

During each `EPOCH`:

1. Generate `nce` counterfactuals and distribute across mini-batches.
2. For each batch compute:
    - Classifier loss: $\ell_{\text{clf}}(f(x),y)$
    - Generator loss: $\ell_{\text{gen}}(x^\prime,x)$
    - Adversarial loss: $\lambda_{\text{adv}} \ell_{\text{clf}}(f(x^\prime),y)$
3. Backpropagate all losses and update parameters.
